Table on stock change factors per clinate zone

### 2020-12-10 ResultNotebooks/results_SOCscenario.Rmd
mayor update on figures and flowfig

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrSOCbudget)
library(magpiesets)

rev <- "rev0.76baseline"

@@

#revisions   <- c(Baseline="rev0.74baseline", Till="rev0.74tillage_mixedtill", ResRe="rev0.74residue_freeze1975", ManRe="rev0.74manure_freeze1975", Yield="rev0.74yield_freeze1975")
filesNeeded <- c("SoilCarbon.rds","Landuse.rds")

revisions   <- c(Baseline="rev0.76baseline", Allon="rev0.76allon_freeze1975", Allon2="rev0.76allon2_freeze1975",        ResRe="rev0.76rrecycle_freeze1975",
                Till="rev0.76tillage_mixedtill", ResSta="rev0.76residue_freeze1975", Yield="rev0.76yield_freeze1975", ManRe="rev0.76manure_freeze1975")

# for(item in revisions){
#    dir.create(path=paste0("Data/",names(which(revisions[]==item))))
#    untar(paste0(getConfig("outputfolder"),"/",item, "_h12_carbonbudget.tgz"), files=filesNeeded, exdir=paste0("Data/", names(which(revisions[]==item))))#, extras="--keep-newer-files ")
# }

outputdir <- "Output/Images"

@@

```{r Carbon Emissions (glo)}

library(ggplot2)

@@

for(r in 1:length(revisions)){
  SoilCarbon <- read.magpie(paste0("Data/",names(revisions[r]),"/SoilCarbon.rds"))
  Landuse    <- read.magpie(paste0("Data/",names(revisions[r]),"/Landuse.rds"))
  SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
  SOCStock        <- toolConditionalReplace(dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2), "is.nan()",0)
  glo_SOCStock    <- mbind(glo_SOCStock, add_dimension(dimSums(SOCStock, dim=1), dim=3.1, nm=names(revisions[r]), add="scenario")) 
}

# 
```

```{r plot Carbon Emissions (glo)}

plot_rev <- c(3,5,6,8)

names(revisions) <- c("Historical Management", 
                      "Allon",    
                      "Constant management from 1975",   
                      "ResRe", 
                      "Constant tillage area from 1975",
                      "Constant residue input from 1975",
                      "Yield", 
                      "Constant manure application from 1975")

colr <- c("black","green","red","brown","pink","darkgreen","yellow","blue")
glo_SOCEmission <- collapseNames(glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000
glo_SOCShare    <- collapseNames( toolConditionalReplace(glo_SOCStock[,,"actualstate"]/glo_SOCStock[,,"naturalstate"], "is.na()",0) )

getNames(glo_SOCEmission) <- names(revisions)
plot(getYears( glo_SOCEmission, as.integer = TRUE), -glo_SOCEmission[,,1], type="l", xlab="Time", ylab="Global SOC gap in GtC", ylim=c(-45,-35))
legend("topleft", legend=names(revisions[c(1,plot_rev)]), col=colr[c(1,plot_rev)], lty=1, cex=0.8)
for(r in plot_rev) lines(getYears(glo_SOCEmission, as.integer = TRUE), -glo_SOCEmission[,,names(revisions[r])], type="l", col=colr[r])
print(cbind(colr[c(1,plot_rev)], names(revisions[c(1,plot_rev)])))
print(glo_SOCStock[,,"actualstate"])

#plot(getYears( glo_SOCEmission, as.integer = TRUE), dimSums(Landuse[,,"crop"], dim=1), type="l")
#plot(getYears( glo_SOCEmission, as.integer = TRUE), dimSums(glo_SOCStock[,,"Baseline.actualstate"], dim=1), type="l")

@@

```{r ggplot}

legend_size <- 10

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,5),c(1,plot_rev)]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = "Global SOC gap in GtC",
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits = c(-45,-35),
                     breaks = c(-36, -38, -40,- 42, -44)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8))

SOCemis

ggsave(paste0(outputdir,"/scenario.png"), plot=SOCemis)

@@

>>>>

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrsoil)
library(magpiesets)

rev <- "rev0.11"

@@

filesNeeded <- c("SoilCarbon.rds","Landuse.rds")

scenarios    <- c("histManagement","constManagement-1975", "constTillage-mixedtill", "constResidues-1975", "constManure-1975",
                  "constManagement2-1975", "constResrate-1975", "constYield-1975",
                 "Initial-natveg", "Initial-natveg_constManagement-1975", "Initial-natveg_constManagement2-1975", 
                 "LitterPNV-PerennialGrasses", "LitterPNV-AASS", "LitterPNV-BRCF", 
                 "LitterPNV-MTCF", "LitterPNV-BLEAF",  "LitterPNV-TREF")

# untar(paste0(getConfig("outputfolder"),"/", rev, "histManagement_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")
# 
for(item in scenarios[10:11]){
   untar(paste0(getConfig("outputfolder"),"/", paste0(rev,item), "_h12_carbonbudget.tgz"),
   files=filesNeeded, exdir=paste0("Data/", item), extras="--keep-newer-files ")
}

outputdir <- "Output/"

@@

```{r Load data and calc globals}

@@

for(scen in scenarios){
  SoilCarbon <- read.magpie(paste0("Data/", scen, "/SoilCarbon.rds"))
  Landuse    <- read.magpie(paste0("Data/", scen, "/Landuse.rds"))
  SoilCarbon[,,"naturalstate.crop"] <- SoilCarbon[,,"naturalstate.natveg"]
  SOCStock        <- toolConditionalReplace(dimSums(dimSums(SoilCarbon[,,"state",pmatch=TRUE], dim=3.3)* Landuse, dim=3.2), "is.nan()",0)
  glo_SOCStock    <- mbind(glo_SOCStock, add_dimension(dimSums(SOCStock, dim=1), 
                                                       dim=3.1, nm=scen, add="scenario")) 
}

glo_SOCDebt  <- collapseNames(glo_SOCStock[,,"naturalstate"] - glo_SOCStock[,,"actualstate"])/1000
glo_SOCShare <- collapseNames(toolConditionalReplace(glo_SOCStock[,,"actualstate"]/glo_SOCStock[,,"naturalstate"], "is.na()",0) )

saveRDS(mbind(add_dimension(collapseNames(glo_SOCStock[,,"actualstate"]), dim=3.1, add="type", nm="stock"),
              add_dimension(              glo_SOCDebt,                    dim=3.1, add="type", nm="debt"),
              add_dimension(              glo_SOCShare,                   dim=3.1, add="type", nm="share")), 
        paste0(outputdir, "glo_SOCscenarions.rds"))
```

```{r Carbon inputs (glo)}

CarbonInput  <- read.magpie(paste0("Data/histManagement/CarbonInput.rds"))
glo_SOCInput <- collapseNames(dimSums(CarbonInput[,,"totalC"] * Landuse, dim=c(1)))

ci2plot <- c('Above Ground Residues'="ag.crop",          
             'Below Ground Residues'="bg.crop",          
             'Manure from Monogastrics'="livst_chick.crop",
             'Manure from Monogastrics'="livst_egg.crop",
             'Manure from Monogastrics'="livst_pig.crop",
             'Manure from Ruminants'="livst_milk.crop",  
             'Manure from Ruminants'="livst_rum.crop",   
             'Natural Litterfall and Fine Roots'="litfall.natveg")

glo_SOCInput <- toolAggregate(glo_SOCInput, rel=data.frame(from=ci2plot,to=names(ci2plot)), from="from", to="to", dim=3)

@@

```{r Plot Management Scenarios}

readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))

manage_scen <-  c(histManagement   = "histManagement",
                  constTillage     = "constTillage-mixedtill", 
                  constManure      = "constManure-1975",
                  constResidues    = "constResidues-1975", 
                  constManagement  = "constManagement-1975")

library(ggplot2)
library(scales)
library(gridExtra)
library(cowplot)

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#648FFF","#785EF0","#DC267F","#FE6100","#FFB000")[5:1]
input_cols  <- scen_cols[1:4]

limits <- c(-30,-21)
breaks <- c(-22, -24,- 26, -28, -30)

hSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),manage_scen]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = "Global SOC debt\n in GtC",
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=scen_cols, labels = names(manage_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="bottom", legend.direction="vertical",
        legend.margin=margin(-10,-10,0,0),
        legend.box.margin=margin(-10,-10,0,0))

hSOCinput <- ggplot(data= as.data.frame(glo_SOCInput[,seq(1975,2010,1),c(3:4,2,1)]),  aes(x = Year, y = Value, group=Data1, fill=Data1)) + geom_area() +
  labs( x = "Year", 
        y = "Global SOC input\n in GtC",
        fill="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous() +
  scale_fill_manual(values=input_cols) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="bottom", 
        legend.direction="vertical",
        legend.margin=margin(-10,-10,0,0),
        legend.box.margin=margin(-10,-10,0,0))

vSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1974,2010,1),manage_scen]),  aes(x = Year, y = Value, group=Data1, color=Data1)) +
  labs( x = "Year", 
        y = "Global SOC debt in GtC",
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits = limits,
                     breaks = breaks) +
  scale_color_manual(values=scen_cols, labels = names(manage_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

vSOCinput <- ggplot(data= as.data.frame(glo_SOCInput[,seq(1975,2010,1),c(3:4,2,1)]),  aes(x = Year, y = Value, group=Data1, fill=Data1)) + geom_area() +
  labs( x = "Year", 
        y = "Global SOC inputs in GtC",
        fill="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous() +
  scale_fill_manual(values=input_cols) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t = 10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size), legend.direction="vertical")

hSOCemis
hSOCinput
vSOCemis
vSOCinput

hgrid <- plot_grid(hSOCemis, hSOCinput, ncol=2, labels=c("(a)","(b)"),
                  label_fontface = "plain", label_size = 10, align="hv")

vgrid <- plot_grid(plot_grid(vSOCemis  + theme(legend.position = "none") , 
                             vSOCinput + theme(legend.position = "none"), ncol=1, labels=c("(a)","(b)"),
                             label_fontface = "plain", label_size = 10, align="v", axis="tblr"),
                   plot_grid(get_legend(vSOCemis), get_legend(vSOCinput), ncol=1,
                             label_fontface = "plain", label_size = 10, align="v"),
                   align="h")

hgrid
vgrid

ggsave(paste0(outputdir,"Images/scenario_horiz.png"), plot=hgrid, width = 15, height = 10, dpi = 300, units = "cm")
ggsave(paste0(outputdir,"Images/scenario_verti.png"), plot=vgrid, width = 12, height = 15, dpi = 300, units = "cm")

@@

```{r Plot Initialization Scenarios}

glo_SOCDebt <- collapseNames(readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))[,,"debt"])

init_scen   <-  c(`histManagement.Initial-natveg`  = "Initial-natveg", 
                  `constManagement.Initial-natveg` = "Initial-natveg_constManagement-1975",
                  `histManagement.Initial-lu`      = "histManagement", 
                  `constManagement.Initial-lu`     = "constManagement-1975")

glo_SOCDebt <- glo_SOCDebt[,,init_scen]
getNames(glo_SOCDebt) <- names(init_scen)

library(ggplot2)
library(scales)
library(gridExtra)
library(cowplot)

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#785EF0","#FE6100","#FFB000")
input_cols  <- scen_cols[1:4]

limits <- c(-30,-10)
breaks <- c(-10, -15,- 20, -25, -30)

initSOCemis <- ggplot() + geom_path(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),]), 
                                    aes(x = Year, y = Value, group=interaction(Data1,Data2), linetype=Data1, color=Data2)) +
  labs( x = "Year", 
        y = "Global SOC debt\n in GtC",
        color    ="Initalitzation",
        linetype ="Management") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c(scen_cols)[1:2], labels = unique(gsub("(.*)\\.(.*)","\\2", names(init_scen)))) +
  scale_linetype_manual(values=c(1,2), labels=unique(gsub("(.*)\\.(.*)","\\1", names(init_scen)))) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position="right", legend.direction="vertical")

initSOCemis

ggsave(paste0(outputdir,"Images/scenario_init.png"), plot= initSOCemis, width = 10, height = 6, dpi = 300, units = "cm")
```

```{r Plot Litter param Scenarios, out.height="6cm", out.width="18cm"}

glo_SOCDebt <- collapseNames(readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))[,,"debt"])
glo_SOCStock <- collapseNames(readRDS(paste0(outputdir, "glo_SOCscenarions.rds"))[,,"stock"])

litter_scen <-  c(`LitterPNV-Mean` = "histManagement",
                  `LitterPNV-grass`= "LitterPNV-PerennialGrasses", 
                  `LitterPNV-AASS` = "LitterPNV-AASS", 
                  `LitterPNV-BRCF` = "LitterPNV-BRCF", 
                  `LitterPNV-MTCF` = "LitterPNV-MTCF", 
                  `LitterPNV-BLEAF`= "LitterPNV-BLEAF",  
                  `LitterPNV-TREF` = "LitterPNV-TREF")

library(ggplot2)
library(scales)
library(gridExtra)
library(cowplot)

theme_set(theme_bw())
legend_size <- 10
scen_cols   <- c("#648FFF","#785EF0","#DC267F","#FE6100","#FFB000")[5:1]
input_cols  <- scen_cols[1:4]

limits <- c(-30,-18)
breaks <- c(-18, -22, -26, -30)

litterSOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCDebt[,seq(1975,2010,1),litter_scen]), 
                                    aes(x = Year, y = Value, group=Data1, color=Data1, size=Data1)) +
  labs( x = "Year", 
        y = "Global SOC debt\n in GtC",
        color="") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c("red", scen_cols, "blue"), labels = names(litter_scen)) +
  scale_size_manual(values=c(1,rep(0.5, length(litter_scen)-1)), labels = names(litter_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.position = "none")

litterSOCemis

limits <- c(625,705)
breaks <- c(635, 655, 675, 695)

litterSOCstock <- ggplot() + geom_line(data= as.data.frame(glo_SOCStock[,seq(1975,2010,1),litter_scen]/1000), 
                                    aes(x = Year, y = Value, group=Data1, color=Data1, size=Data1)) +
  labs( x = "Year", 
        y = "Global SOC stock\n in GtC",
        color="Litter parameterization",
        size="Litter parameterization") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(limits=limits, breaks=breaks) +
  scale_color_manual(values=c("red", scen_cols, "blue"), labels = names(litter_scen)) +
  scale_size_manual(values=c(1,rep(0.5, length(litter_scen)-1)), labels = names(litter_scen)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size, margin = margin(t = 0, r =10, b = 0, l = 0, unit = "pt")),
        axis.title.x= element_text(size=legend_size, margin = margin(t =10, r = 0, b = 0, l = 0, unit = "pt")),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8, size=legend_size),
        legend.direction="vertical",
        legend.margin=margin(-10,-10,0,0),
        legend.box.margin=margin(-10,-10,0,0)) +
  guides(color=guide_legend(), size = guide_legend())

litterSOCstock

littergrid <- plot_grid(litterSOCemis, litterSOCstock + theme(legend.position = "none"), get_legend(litterSOCstock),
                                  ncol=3, labels=c("(a)","(b)"), axis = "l",
                                  label_fontface = "plain", label_size = 10, align="v")
littergrid

ggsave(paste0(outputdir,"Images/scenario_litter.png"), plot=littergrid, width = 18, height = 6, dpi = 300, units = "cm")

### 2020-12-10 ResultNotebooks/results_SOCtable.Rmd
mayor update on figures and flowfig

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrSOCbudget)
library(magpiesets)

rev <- "rev0.6_mrSOC"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Landuse.rds")

@@

koeppen           <- readSource("Koeppen", subtype="cellular", convert="onlycorrect" )
getNames(koeppen) <- tolower(getNames(koeppen))
koepp2IPCC        <- toolGetMapping("mapping_koeppen_ipcc.csv", type = "sectoral")
koepp2IPCC$koeppen_geiger <- tolower(koepp2IPCC$koeppen_geiger)
climateIPCC       <- toolAggregate(koeppen, rel=koepp2IPCC, from="koeppen_geiger", to="ipcc_reduced", dim=3)
climateIPCC       <- climateIPCC[,getYears(SoilCarbon),]

rm(koeppen)

SOCDens           <- dimSums(SoilCarbon[,,c("steadystate","actualstate","naturalstate")], dim=3.3) 
SOCDens[,,"naturalstate.crop"] <- SOCDens[,,"actualstate.crop"]

CShare_ipcczone   <- dimSums(climateIPCC * SOCDens[,,"crop"]   * Landuse[,,"crop"], dim=1)/
                     dimSums(climateIPCC * SOCDens[,,"natveg"] * Landuse[,,"crop"], dim=1)

print(collapseNames(CShare_ipcczone[,findset("past"),]))

actualstate_table  <- data.frame(dcast(as.data.frame(collapseNames(CShare_ipcczone[,findset("past"),"actualstate"])), 
                            Year ~ Data1, value.var="Value", row.names=findset("past")), row.names = "Year")

naturalstate_table  <- data.frame(dcast(as.data.frame(collapseNames(CShare_ipcczone[,findset("past"),"naturalstate"])), 
                            Year ~ Data1, value.var="Value", row.names=findset("past")), row.names = "Year")

steadystate_table  <- data.frame(dcast(as.data.frame(collapseNames(CShare_ipcczone[,findset("past"),"steadystate"])), 
                            Year ~ Data1, value.var="Value", row.names=findset("past")), row.names = "Year")

saveRDS(list(naturalstate_table = naturalstate_table,
             actualstate_table  = actualstate_table, 
             steadystate_table  = steadystate_table), "Output/SFC_climatezone.rds")

#knitr::kable(naturalstate_table, "latex",digits=2, label="naturalstate_table")
#knitr::kable(actualstate_table, "markdown", digits=2)
```

@@

CShare_ipcc <- new.magpie("GLO","y2010",outer(c("IPCC2006","IPCC2019"),unique(koepp2IPCC$ipcc_reduced), paste, sep="."))

CShare_ipcc[,,"IPCC2006.tropical_moist"]  <- "0.48"
CShare_ipcc[,,"IPCC2006.tropical_dry"]    <- "0.58-0.64" 
CShare_ipcc[,,"IPCC2006.temperate_moist"] <- "0.69"
CShare_ipcc[,,"IPCC2006.temperate_dry"]   <- "0.80"

CShare_ipcc[,,"IPCC2019.tropical_moist"]  <- "0.83"
CShare_ipcc[,,"IPCC2019.tropical_dry"]    <- "0.92" 
CShare_ipcc[,,"IPCC2019.temperate_moist"] <- "0.69-0.70"
CShare_ipcc[,,"IPCC2019.temperate_dry"]   <- "0.76-0.77"

comparison <- mbind(CShare_ipcc, 
                    round(add_dimension(collapseNames(CShare_ipcczone[,"y2010","naturalstate"]),
                                  add="SOCbudget",nm="model"),2))

print(dimOrder(comparison[,,sort(getNames(comparison,dim=1))], c(2,1)))

@@

>>>>

```{r load}
library(mrcommons)
library(mrvalidation)
library(mrsoil)
library(magpiesets)

rev       <- "rev0.11"
outputdir <- "Output/"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data/histManagement", extras="--keep-newer-files ")

SoilCarbon <- read.magpie(paste0("Data/histManagement/SoilCarbon.rds"))[,1975:2010,]
Landuse    <- read.magpie(paste0("Data/histManagement/Landuse.rds"))[,1975:2010,]

@@

library(knitr)
library(stats)
library(reshape2)

years             <- intersect(findset("past"), getYears(SoilCarbon))

### calculating climate mask
koeppen           <- readSource("Koeppen", subtype="cellular", convert="onlycorrect" )[,years,]
koepp2IPCC        <- toolGetMapping("mapping_koeppen_ipcc.csv", type = "sectoral")
getNames(koeppen)         <- tolower(getNames(koeppen))
koepp2IPCC$koeppen_geiger <- tolower(koepp2IPCC$koeppen_geiger)
climateIPCC       <- toolAggregate(koeppen, rel=koepp2IPCC, from="koeppen_geiger", to="ipcc_reduced", dim=3)
rm(koeppen)

### calculating stock change factors
SOCDens           <- dimSums(SoilCarbon[,years,c("actualstate","naturalstate")], dim=3.3) 
SOCDens[,,"naturalstate.crop"] <- SOCDens[,,"actualstate.crop"]

CShare_ipcczone   <- dimSums(climateIPCC * SOCDens[,,"crop"][,,"actualstate"]   * Landuse[,years,"crop"], dim=1)/
                     dimSums(climateIPCC * SOCDens[,,"natveg"][,,"naturalstate"] * Landuse[,years,"crop"], dim=1)

getNames(CShare_ipcczone) <- gsub("_", " ", getNames(CShare_ipcczone))

SCF_table  <- data.frame(dcast(as.data.frame(collapseNames(CShare_ipcczone[,years,"naturalstate"])), 
                             Year ~ Data1, value.var="Value", row.names=years), row.names = "Year")
saveRDS(list(SCF_table = SCF_table), paste0(outputdir, "SFC_climatezone.rds"))

knitr::kable(SCF_table, "latex",digits=2, label="naturalstate_table")

```{r plot climte map}

magpie_coord  <- toolGetMapping("magpie_coord.rda", type="cell")
climate2plot <- dimSums(climateIPCC*new.magpie("GLO",NULL,getNames(climateIPCC),c(1:4)), dim=3)
climate2plot <- merge(as.data.frame(climate2plot), data.frame(magpie_coord, Cell=c(1:59199)), by="Cell")

library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(RColorBrewer)
library(sp)
library(rworldmap)
library(oce) 
library(scales)

legend_size <- 10

map.world <- map_data("world")
world         <- ne_countries(scale = "medium", returnclass = "sf")
data(coastlineWorld)  
coastline.world <- data.frame(longitude=coastlineWorld[["longitude"]],latitude=coastlineWorld[["latitude"]])

cols          <- colorRampPalette(brewer.pal(4, "RdYlBu"))(4)

ClimateZones <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(climate2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = factor(Value))) +
    scale_fill_manual(name = expression("climate zones"), 
                      values = cols, na.value = "white",
                      breaks= c(1,2,3,4),
                      labels = gsub("_", " ", getNames(climateIPCC)),
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7)),
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")
          )
ClimateZones 
ggsave(paste0(outputdir,"/climatezones.png"), plot=ClimateZones , width = 10, height = 7, dpi = 300, units = "cm")
```

@@

MShare_ipcc <- LShare_ipcc <-  HShare_ipcc <- new.magpie("GLO",NULL,outer(c("IPCC2006","IPCC2019"),
                                                                          unique(koepp2IPCC$ipcc_reduced), paste, sep="."))

MShare_ipcc <- add_dimension(MShare_ipcc, dim=3.2, nm="medium.invariant", add="input.year")
LShare_ipcc <- add_dimension(LShare_ipcc, dim=3.2, nm="low.invariant",    add="input.year")
HShare_ipcc <- add_dimension(HShare_ipcc, dim=3.2, nm="high.invariant",   add="input.year")

MShare_ipcc[,,"IPCC2006.medium"][,,"tropical_moist"]  <- "0.48"
MShare_ipcc[,,"IPCC2006.medium"][,,"tropical_dry"]    <- "0.58--0.64" 
MShare_ipcc[,,"IPCC2006.medium"][,,"temperate_moist"] <- "0.69"
MShare_ipcc[,,"IPCC2006.medium"][,,"temperate_dry"]   <- "0.80"

MShare_ipcc[,,"IPCC2019.medium"][,,"tropical_moist"]  <- "0.83"
MShare_ipcc[,,"IPCC2019.medium"][,,"tropical_dry"]    <- "0.92" 
MShare_ipcc[,,"IPCC2019.medium"][,,"temperate_moist"] <- "0.69--0.70"
MShare_ipcc[,,"IPCC2019.medium"][,,"temperate_dry"]   <- "0.76--0.77"

#Low input regime factor
LShare_ipcc[,,"IPCC2006.low"][,,"tropical_moist"]  <- "0.44"
LShare_ipcc[,,"IPCC2006.low"][,,"tropical_dry"]    <- "0.55--0.61" 
LShare_ipcc[,,"IPCC2006.low"][,,"temperate_moist"] <- "0.66"
LShare_ipcc[,,"IPCC2006.low"][,,"temperate_dry"]   <- "0.74"

LShare_ipcc[,,"IPCC2019.low"][,,"tropical_moist"]  <- "0.76"
LShare_ipcc[,,"IPCC2019.low"][,,"tropical_dry"]    <- "0.87" 
LShare_ipcc[,,"IPCC2019.low"][,,"temperate_moist"] <- "0.66--0.67"
LShare_ipcc[,,"IPCC2019.low"][,,"temperate_dry"]   <- "0.70--0.71"

#High input regime factor
HShare_ipcc[,,"IPCC2006.high"][,,"tropical_moist"]  <- "0.53"
HShare_ipcc[,,"IPCC2006.high"][,,"tropical_dry"]    <- "0.60--0.67" 
HShare_ipcc[,,"IPCC2006.high"][,,"temperate_moist"] <- "0.77"
HShare_ipcc[,,"IPCC2006.high"][,,"temperate_dry"]   <- "0.83"

HShare_ipcc[,,"IPCC2019.high"][,,"tropical_moist"]  <- "0.92"
HShare_ipcc[,,"IPCC2019.high"][,,"tropical_dry"]    <- "0.96" 
HShare_ipcc[,,"IPCC2019.high"][,,"temperate_moist"] <- "0.77--0.78"
HShare_ipcc[,,"IPCC2019.high"][,,"temperate_dry"]   <- "0.79--0.80"

CShare_ipcc <- mbind(LShare_ipcc,MShare_ipcc,HShare_ipcc)
getNames(CShare_ipcc) <- gsub("_", " ", getNames(CShare_ipcc))

comparison <- mbind(CShare_ipcc, 
                    round(add_dimension(setYears(collapseNames(CShare_ipcczone[,"y1990","naturalstate"]),NULL),
                                  nm="This Study.hist.1990",add="model.input.year"),2),
                    round(add_dimension(setYears(collapseNames(CShare_ipcczone[,"y2010","naturalstate"]),NULL),
                                  nm="This Study.hist.2010",add="model.input.year"),2))

#print(dimOrder(comparison[,,sort(getNames(comparison,dim=1))], c(2,1)))

comparison_table  <- data.frame(dcast(as.data.frame(collapseNames(comparison)), 
                           Data1 + Data2 + Data3 ~ Data4, value.var="Value", 
                            row.names=levels(as.data.frame(comparison)$Data1)))

colnames(comparison_table) <- gsub("\\.", " ", colnames(comparison_table))
colnames(comparison_table)[1:3] <- c("Source", "Input", "Year")

saveRDS(list(comparison_table = comparison_table), paste0(outputdir,"SFC_comparison.rds"))

@@

```{r kable2image}
library(kableExtra)

getwd()
table <- readRDS(paste0(outputdir,"/SFC_comparison.rds"))

save  <- kbl(table$comparison_table, latex = T, digit=2)%>%
            kable_styling(latex_options = c("scale_down","striped"), full_width = F)%>%
              row_spec(7:8, bold=TRUE)

save_kable(save, file="Output/Images/TableSCF_comparison.png")
```
